\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-01-12 doc/publications/plos16/plos16.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 2: Feature Selection on real data 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\cursedforest selects previously demonstrated cancer variants}
We consider the question of feature discovery on the Cancer Genome Atlas (TCGA) BRCA dataset.  We build this model on
VCF files retrieved from the TCGA data portal.  For the label, we use the cell type, tumor or normal.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 2: Feature Selection on real data 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\cursedforest\ selects previously demonstrated bone-density variants}
We consider the problem of feature discovery on a genomic dataset for a specific phenotype.
In this case we investigate the ability of  ability to locate variants in the same loci as genes previously demonstrated to
be associated with a high or low bone mass density (BMD) and rank these variants as being "important".
From a random forest model built on this data, we produce a list of the to 5,000 features. 
Applying the Mann–Whitney U test to these fetures we observe a p-value of x, supporting our
hypothesis that features in close proximity to the known BMD genes are Contributing more information to our classification model.

One observation we make is that of the most-important features---for example, the top ten variants ranked by Gini impurity---is
that not all of these are variants are in close proximity of known BMD genes.
One of these is COLEC10. Featuring a transcription factor binding site for FOXL1, COLEC10 is also reported as containing a SNP
associated with BMD \cite{Liu2008}.
